---
title: "block pricing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Makecondition

```{r makecondition}
library(reticulate)
use_condaenv("r-reticulate")

library(econR) # 經濟模型程式設計專題用
```

## Install packages

Through Conda:

```{r, eval=F}
conda_install("r-reticulate",
              packages=c("numpy", "pandas"))
```

```{r, eval=F}
conda_install("r-reticulate",
              packages=c("scipy", "pandas"))
```

## Codes

#1.Under uniform price situation 以一般數值算式求解
```{python}
class Monopoly:  #under uniform price situation
    intercept = 200  # the demand curve's intercept (firm's faced)
    slope = 0.5      # the demand curve's slope (firm's faced)
    
    def __init__(self, mc): #assumed there are no fixed cost
        self.mc = mc
    def p(self, mc):
        return self.__class__.intercept - self.__class__.slope * self.__class__.Qd(mc)
    def profit(self, mc):
        return (self.p(mc) - mc) * self.__class__.Qd(mc)
    
    @classmethod
    def Qd(cls, mc):
        return (cls.intercept - mc)/(cls.slope * 2)

```

```{python}
mc = 50   #為alterable,可改變 marginal cost看整體影響
monopoly1 = Monopoly(mc) # only need to give marginal cost

monopoly1.mc
monopoly1.Qd(mc)
monopoly1.p(mc)
monopoly1.profit(mc)

```

#1-2.如果使用optimize.minimize求解?
```{python}
from scipy import optimize
import numpy as np

```

```{python}
class retryMonopoly:
    intercept = 400  #原式為 p=200-0.5Q 換邊得 Q=400-2p
    slope = 2
    
    def __init__(self, mc):
        self.mc = mc
    
    def profit(self, p):
        return p * self.__class__.Qd(p) - self.mc * self.__class__.Qd(p)
    def optimize(self, x0=2):
        optim_result = optimize.minimize(
          fun=negative_conversion(self.profit),
          x0=np.array([x0])
        )
        self.optim_p = optim_result.x
        self.optim_q = self.__class__.Qd(self.optim_p)
        return optim_result
    def consumersurplus(self, mc): #之後和兩部定價比較會用到(for inheritance)
        return (self.optim_p - mc) * (self.optim_q)
    
    @classmethod
    def Qd(cls, p):
        return cls.intercept - cls.slope*p

# covert to positive function
def negative_conversion(fn):
    def neg_fun(p):
        return -1*fn(p)
    return neg_fun

```

```{python}
mc = 50   #為alterable,可改變 marginal cost看整體影響
monopoly1 = Monopoly(mc) # only need to give marginal cost

monopoly1.mc
monopoly1.Qd(mc)
monopoly1.p(mc)
monopoly1.profit(mc)

retryMonopoly1 = retryMonopoly(mc)
retryMonopoly1.Qd(monopoly1.p(mc))
retryMonopoly1.profit(monopoly1.p(mc))

retryMonopoly1.optimize()
retryMonopoly1.optim_p  #close to 125
retryMonopoly1.optim_q  #close to 150
                        #最適結果會是一致的

```

#2.Now firm want's to improve its profits by implementing block pricing.
#  suppose the company were to sell the first block at the price determined in the uniform price situation.
#(即給定p1、Q1為上面所解出的p、q，求算第二區塊之定價和產量以及block pricing下之extra profit)

#2-1.以一般數值算式求解block pricing(First block price and quantity were limited.)
```{python}
#此時p1 = 125, Q1 = 150,求p2,Q2 (如果有改數字就不會是這個狀況，不過這裡假設如此)

class Twoblocks:
    intercept = 200  # the demand curve's intercept (firm's faced)
    slope = 0.5      # the demand curve's slope (firm's faced)
    
    def __init__(self, mc): #assumed there are no fixed cost
        self.mc = mc
    def p(self, mc):
        return self.__class__.intercept - self.__class__.slope * (monopoly1.Qd(mc)+self.__class__.Qd(mc))
    def profit(self, mc):
        return (self.p(mc) - mc) * self.__class__.Qd(mc)
    
    @classmethod
    def Qd(cls, mc):
        return (cls.intercept - (cls.slope * monopoly1.Qd(mc)) - mc )/(cls.slope * 2)

```

```{python}
mc = 50  # 為alterable,可改變 marginal cost看整體影響
twoblock1 = Twoblocks(mc)

twoblock1.mc # face the same marginal cost = 50
twoblock1.Qd(mc) # second block's profit maximizing quantity
twoblock1.p(mc)  # second block's profit maximizing price
twoblock1.profit(mc)

totalprofit = monopoly1.profit(mc) + twoblock1.profit(mc) #兩區塊定價後的總收益(第一區塊的價格及產量被限制下)
totalprofit

```

#2-2.同樣如果使用optimize.minimize求解?
```{python}
class retryTwoblocks:
    intercept = 400  #原式為 p=200-0.5Q 換邊得 Q=400-2p
    slope = 2
    
    def __init__(self, mc):
        self.mc = mc
    
    def profit(self, p):
        return p * self.__class__.Qd(p) - self.mc * self.__class__.Qd(p)
    def optimize(self, x0=2):
        optim_result = optimize.minimize(
          fun=negative_conversion(self.profit),
          x0=np.array([x0])
        )
        self.optim_p = optim_result.x
        self.optim_q = self.__class__.Qd(self.optim_p)
        return optim_result
    
    @classmethod
    def Qd(cls, p):
        return cls.intercept - cls.slope*p - retryMonopoly1.Qd(monopoly1.p(mc))

# covert to positive function
def negative_conversion(fn):
    def neg_fun(p):
        return -1*fn(p)
    return neg_fun

```

```{python}
mc = 50

twoblock1 = Twoblocks(mc)

twoblock1.mc # face the same marginal cost = 50
twoblock1.Qd(mc) # second block's profit maximizing quantity
twoblock1.p(mc)  # second block's profit maximizing price
twoblock1.profit(mc)

retryTwoblocks1 = retryTwoblocks(mc)
retryTwoblocks1.Qd(twoblock1.p(mc))
retryTwoblocks1.profit(twoblock1.p(mc))

retryTwoblocks1.optimize()
retryTwoblocks1.optim_p  #close to 87.5
retryTwoblocks1.optim_q  #close to 75

retrytotalprofit = retryMonopoly1.profit(monopoly1.p(mc)) + retryTwoblocks1.profit(twoblock1.p(mc))
retrytotalprofit #兩區塊定價後的總收益(第一區塊的價格及產量被限制下)

```

#3.Now the company wants to earn more profit with a set of prices and quantities for the two blocks.
#  that's no given situation for the company,just maximize profit by block pricing.

#3-1.block pricing.(Pursuing maximize profit without limited.)
```{r, eval=F}
conda_install("r-reticulate",
              packages=c("sympy", "pandas"))
```

```{python}
# demand curve and marginal cost set up or question required.(Assumed no fixed cost.)

#在此可依據題意要求來更改所面臨之需求曲線之截距、斜率，以及所面臨的邊際成本。
intercept = 200 #alterable
slope = 0.5 #alterable
mc = 50 # alterable

```

```{python}
import sympy as sym
from sympy import solve, linsolve, symbols, Matrix, Eq, diff

```

```{python}

#target => max profit function = (intercept-slope * Q1 -mc) * Q1 + (intercept-slope * Q2 -mc) * (Q2-Q1)

Q1, Q2 = symbols('Q1 Q2')
focQ1 = diff((intercept-slope * Q1 -mc) * Q1 + (intercept-slope * Q2 -mc) * (Q2-Q1), Q1) #對Q1微
focQ2 = diff((intercept-slope * Q1 -mc) * Q1 + (intercept-slope * Q2 -mc) * (Q2-Q1), Q2) #對Q2微

eq1 = Eq(focQ1)
eq2 = Eq(focQ2)
sol = solve([eq1, eq2], dict=True)

sol[0][Q1] # first block output
sol[0][Q2] # second block output


p1 = intercept - slope * sol[0][Q1] #代回原需求函數中求得價格
p1 #first block price

p2 = intercept - slope * sol[0][Q2]
p2 #second block price

```

```{python}
blockpricingtotalprofit = (p1-mc) * (sol[0][Q1]) + (p2-mc) * (sol[0][Q2]-sol[0][Q1])
blockpricingtotalprofit #block pricing下極大化總收益 note:可觀察到也會大於被限制下使用兩區塊定價後的總收益

```

#4 Two-part tariff(subscription and usage charge)
# How to set the entry fee(T) and the per-unit usage charge(P)?
# For simplicity,suppose all consumers are alike, each having a demand for telephone services as follows.

#4-1. two-part tariff:
```{python}
#Assume the firm has a constant marginal cost of 50 and demand curve is...
class Twoparttariff:
    intercept = 20.05 #Assume
    slope = 1 #Assume
    def __init__(self, mc):
        self.mc = mc
    def profit(self, mc):
        return 1/2 * (self.__class__.intercept-mc) * (self.__class__.intercept - mc) #此時p* = mc = 0.05

#The concept of entry fee and a usage charge:為了能夠最大化的拿走全部的CS(消費者剩餘)，利用block pricing的方式一塊一塊的取走，最終價格p會定在mc為其最適定價，而後用entry fee(T)取走所有的CS.
#故#此時p* = mc = 0.05
```

```{python}
mc = 0.05 #Assume marginal cost = 0.05
Twoparttariff1 = Twoparttariff(mc)
Twoparttariff1.profit(mc)

```

#4-2. Compare to when under simple monopoly pricing:
```{python}
class simpleMonopoly(retryMonopoly): #inheritance
    intercept = 20.05  #原式為 p=200-0.5Q 換邊得 Q=400-2p
    slope = 1
    
    def __init__(self, mc):
        self.mc = mc

```

```{python}
mc = 0.05 #Assume marginal cost = 0.05
simpleMonopoly1 = simpleMonopoly(mc)
simpleMonopoly1.Qd(mc)
simpleMonopoly1.profit(mc)  #這裡的廠商profit會變成0,but他們的新收入是消費者的所有CS.

simpleMonopoly1.optimize()
simpleMonopoly1.optim_p #最適定價為10.05
simpleMonopoly1.optim_q #最適產量為10

simpleMonopoly1.consumersurplus(mc) #廠商的新CS

```

#雖然數字有設計過，但可以發現這裡透過two-part tariff profit為200，而在面臨同樣地需求曲線和mc下，under simple monopoly下以MR=MC下求得profit為100，可以發現已經落差2倍了。
#Note: in the real world, the firm cannot easily capture all the consumer surplus.

